\cvsection{Projects Experience}
\begin{cventries}

%%% Online Web Application %%%
    \cventry
  	{Keywords: Angular5,Material2,Rxjs,NestJs,TypeORM,Postgres,D3.JS,Ng-charts} % position
    {Pittsburgh's Community Medical Center Web Project} % name
    {University of Pittsburgh,PA} % location
    {Aug 2017 - Jun 2018}  % date range
    {
      \begin{cvitems}
      	\item {Designed and developed an community medical center web application with visualization analytics by utilizing similar-MEAN framework.}
        \item {Utilized Angular5 and Material2 component Library to develop front-end web page, implemented RXJS optimizing service with back-end connecting, applied Lazy-loading technique to implement multi-level user login, Utilized Reactive\&dynamic Form and Control\&ValueAccessor to implement business form and universal form.}
        \item {Utilized NestJs framework which is based on NodeJs-MVC to build back-end server, implemented TypeORM to bridge the connection between server and Postgres database, took advantage of modularity and dependency injection to reduce the coupling between modules.}
        \item {Designed data visualization solution for patients' data analysis,and utilized D3.js,ng-charts2 and Echarts4Angular to build force-layout graph, scatter-plot graph,pie-chart graph and heat-map to demonstrate patients' health in community in different perspectives.}
	    \item {\href{https://www.youtube.com/watch?v=qYdQ3TKAbvE&t=3s}{Demo Video}}
%         \item {	Deployed the system on AWS}
      \end{cvitems}
    }

%%%Dynamic Visualization%%%
  \cventry
   	{Keywords: Angular5,Material2,NestJs,TypeORM,MySQL} % position
    {Southwestern Pennsylvania Environmental Health Project} % name
    {Pittsburgh,PA} % location
    {Feb 2018 - May 2018}  % date range
    {
      \begin{cvitems}
      	\item {Designed and developed an light weight environment data interaction system by utilizing Angular5 and NestJs.}
        \item {Utilized Angular5 framework and Material2 implements interactive front-end page to display environmental health data.}
        \item {Utilized NestJs based on NodeJs to build MVC style back-end server, applied TypeORM to connect MySQL database, fully embracing TypeScript to reduce the dependencies between modules.}
%         \item { Tried feature selection methods, such as feature ranking and subset selection.}
      \end{cvitems}
    }

    
 %%%Medical Analysis System%%%
      \cventry
    {Keywords: Angular5,Rxjs,Clarity,NestJS,TypeORM,PostgresSQL} % position
    {University of Pittsburgh's HealthU Project} % name
    {University of Pittsburgh,PA} % location
    {Apr 2018 - May 2018}  % date range
    {
      \begin{cvitems}
      % \item {Designed and implemented an interactive system for recommending the answers for Twitter questions.}
      	\item {Designed and implemented an on-line survey system to collect students and faculty's health data.}
		\item {Utilized Angular5 and Vmware-Clarity component library to develop a multi-type user survey, implemented Lazy-Loading technique to fulfill dynamic generating survey.}
        \item {Utilized Ng-charts2 to develop Trending chart, Bar chart and Pie Chart, in order to display users' survey results more intuitively.}
        \item{Utilized NestJs to build the back-end server and implemented TypeORM to connect with Postgres database.}
        \item {\href{https://www.youtube.com/watch?v=BudcaOVT4Yc}{Demo Video}}
%         \item {Represented text as graph using unigram language model and built relations between text and user.}
%         \item {Implemented probability language model and tried various smoothing methods.}
      \end{cvitems}
    }
    
     \cventry
    {Keywords: Angular4,Ionic3,PWA,Flex Box} % position
    {Vocabulary Learning Mobile Project} % name
    {University of Pittsburgh,PA} % location
    {Mar 2018}  % date range
    {
      \begin{cvitems}
      % \item {Designed and implemented an interactive system for recommending the answers for Twitter questions.}
      	\item {Designed and implemented an alpha version Vocabulary learning application.}
		\item {Utilized Angular4,Ionic3 and PWA technology implementing a on-line learning web application which is free installation with direct downloading.}
        \item {Utilized Flex-box layout replace traditional CSS box layout, designed and implemented application's animation More logical.}
        \item {\href{https://fathomless-thicket-29720.herokuapp.com}{Demo address}}
%         \item {Represented text as graph using unigram language model and built relations between text and user.}
%         \item {Implemented probability language model and tried various smoothing methods.}
      \end{cvitems}
    }
    
    \cventry
    {Keywords: Angular4,Material2,Express2,MongoDB,Ng-charts,GoogleMapForAngular} % position
    {City of Pittsburgh's Network Speed Collecting Project} % name
    {University of Pittsburgh,PA} % location
    {Mar 2017 - Sept 2017}  % date range
    {
      \begin{cvitems}
      % \item {Designed and implemented an interactive system for recommending the answers for Twitter questions.}
      	\item {Utilized MEAN framework to design and implement an assessment and visual-analysis system for Pittsburgh city's Internet speed .}
		\item {Utilized Angular4,Material2 component Library to design and implement front-end page including Internet speed test, User survey.}
        \item {Utilized Express2 based on Nodejs to build a Internet speed test web-page with server.Demo \href{https://mysterious-cliffs-71051.herokuapp.com/}{Address}.}
        \item {Utilized GoogleMapForAngular to design and implement a interactive map and applied ng-charts to build pie chat and bar chart purposing to analysis Internet penetration rate and network distribution status in Pittsburgh area.}
%         \item {Implemented probability language model and tried various smoothing methods.}
      \end{cvitems}
    }
    
     \cventry
    {Keywords: HTML,CSS,JavaScript,JQuery,D3.js,Leaflet} % position
    {On-line Analysis system for Pittsburgh Bike sharing Project} % name
    {University of Pittsburgh,PA} % location
    {Oct 2016 - Dec 2016}  % date range
    {
      \begin{cvitems}
      % \item {Designed and implemented an interactive system for recommending the answers for Twitter questions.}
      	\item {Utilized Leaflet map API with normal HTML,CSS and JQuery to design and implement a dynamic and interactive web page.}
		\item {Utilized D3.js to design and implement types of diagram including bar-chart,scatter-plot,time-series graph, exposed the usage distribution from multiple perspectives.}
        \item {\href{http://picso.org:8889/~classinfovis2016fall/projects/group-11/}{Demo address}}
%         \item {Utilized Express2 based on Nodejs to build a Internet speed test web-page with server.Demo \href{https://mysterious-cliffs-71051.herokuapp.com/}{Address}.}
%         \item {Utilized GoogleMap4Angular to design and implement a interactive map and applied ng-charts to build pie chat and bar chart purposing to analysis Internet penetration rate and network distribution status in Pittsburgh area.}
%         \item {Implemented probability language model and tried various smoothing methods.}
      \end{cvitems}
    }
    
    \cventry
    {Keywords: R language,KNN,Ada Boost,Naive Bayesian,Decision Tree,Logistic Regression} % position
    {Data mining for Pittsburgh Bike Sharing Project} % name
    {University of Pittsburgh,PA} % location
    {Mar 2016 - May 2016}  % date range
    {
      \begin{cvitems}
      % \item {Designed and implemented an interactive system for recommending the answers for Twitter questions.}
      	\item {Utilized Data Mining techniques to analyze the Operational status
for Pittsburgh Bike Sharing Project.}
		\item {Utilized data mining algorithms (KNN, Ada Boost, Naive Bayesian, Decision Tree, Logistic Regression) to analyze user data and predict the types of frequent and short clients based on business data.}
%         \item {\href{http://picso.org:8889/~classinfovis2016fall/projects/group-11/}{Demo address}}
%         \item {Utilized Express2 based on Nodejs to build a Internet speed test web-page with server.Demo \href{https://mysterious-cliffs-71051.herokuapp.com/}{Address}.}
%         \item {Utilized GoogleMap4Angular to design and implement a interactive map and applied ng-charts to build pie chat and bar chart purposing to analysis Internet penetration rate and network distribution status in Pittsburgh area.}
%         \item {Implemented probability language model and tried various smoothing methods.}
      \end{cvitems}
    }



%%% Android Application Security Permission Detection System %%%
  \cventry
    {Keywords: Android, APKTOOL, Swing, Regex} % position
    {Android Application Security Permission Detection System} % name
    {University of Pittsburgh,PA} % location
    {Mar 2014 - July 2014}  % date range
    {
      \begin{cvitems}
        \item {Designed and Developed a Java application by Swing to detect the privilege escalation exploits from Android applications .}
         \item {Utilized APKTOOL to decode resource code from Android applications to nearly original form for system detecting privilege escalation exploits by using Regex.}
        \item {Utilized Executor Service to improve the system efficiency by as much as 60\% when detecting the privilege escalation exploits.}
%         \item {Evaluated the performance of system extracted tips by ROUGE and BLUE.}
      \end{cvitems}
    }

% %%% Visualization %%%
%   \cventry
%     {Keywords: Visualization, d3.js, Javascript, HTML, CSS} % keywords
%     {Data Visualization on Contagious Diseases} % subject
%     {} % date
% %     {Oct. 2014 - Dec. 2014}  % date 
%     {} 
%     {
%       \begin{cvitems}
% 		\item {Devised and assembled an interactive visualization system to explore the data of three major contagious diseases.}
%         \item {Implemented interactive front end using Javascript; developed three major methods using d3.js, choropleth, bar chart and line chart, to visualize the change of vaccine data over years and distribution among states.}
%       \end{cvitems}
%     }


% %%% Database project %%%
%     \cventry
%     {Keywords: Java, MySQL, MVC, JSP} % keywords
%     {Online Digital Store} % subject
%     {} % date
% %     {Oct. 2014 - Dec. 2014} % date 
%     {} 
%     {
%       \begin{cvitems}
%         \item {Designed and built an online E-business system to sell digital products by using JSP and Servlet in MVC framework.}
%         \item {Designed E-R diagram, designed and implemented backend database using MySQL according to business needs.}
%         \item {Implemented interactions between front end and back end.}
%       \end{cvitems}
%     }
    
\end{cventries}